### 2014-02-26 paper/retrofit.tex
tini

\begin{mathpar}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
.->
iS'; sched fork (it1, ldots, itnew)
|}

\and
\inferrule[I-done]
{|
|}
{|
iconf iS (fullconf id il tS iv, ldots)
.->
iS ; sched done (fullconf id il tS iv, ldots)
|}

\and
\inferrule[I-noStep]
{|
iconf iS (it, ldots) .-/> 
|}
{|
iconf iS (it, ldots)
.->
iS ; sched noStep (it, ldots)
|}

@@

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |tconf id il' ie| & \text{otherwise}
  \end{cases} \\
  &|erase il nil = nil|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|\\
  &\text{In all other cases, |erasef il| is applied homomorphically.}
\end{align*}
\caption{Erasure function.}
\end{figure}

@@

\begin{figure}
  Round robin:
\begin{code}
  sched step (it1, it2, ...)    = {it2, ..., it1}
  sched done (it1, it2, ...)    = {it2, ...}
  sched noStep (it1, it2, ...)  = {it2, ...}
  sched fork (it1, it2, ...)    = {it2, ..., it1}
\end{code}
  Browbound:
\begin{code}
  sched step (it1, it2, ...)    = {it1, it2, ...}
  sched noStep (it1, it2, ...)  = {it2, ...}
  sched done (it1, it2, ...)    = {it2, ...}
  sched fork (it1, it2, ...)    = {it1, it2, ...}
\end{code}
  Sequential:
\begin{code}
  sched step (it1, it2, ...)       = {it1, it2, ...}
  sched noStep (it1, it2, ...)     = {it1, it2, ...}
  sched done (it1, it2, ...)       = {it2, ...}
  sched fork (it1, it2, ... it1n)  = {itn, it1, it2, ...}
\end{code}
\caption{Scheduling policies}
\end{figure}

@@

>>>>

\begin{mathpar}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
.->
iS'; sched F (it1, ldots, itnew)
|}

\and
\inferrule[I-done]
{|
|}
{|
iconf iS (fullconf id il tS iv, ldots)
.->
iS ; sched D (fullconf id il tS iv, ldots)
|}

\and
\inferrule[I-noStep]
{|
iconf iS (it, ldots) .-/> 
|}
{|
iconf iS (it, ldots)
.->
iS ; sched N (it, ldots)
|}

@@

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |tconf id il' ie| & \text{otherwise}
  \end{cases} \\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|
\end{align*}
\caption{
Erasure function for configurations, threads, system state, and
message queus.  In all other cases, |erasef il| is applied
homomorphically.
\label{fig:erasure}
}
\end{figure}

@@

\begin{figure}
  Concurrent, round robin:
\begin{code}
  sched S (it1, it2, ldots)  = it2, ldots, it1
  sched D (it1, it2, ldots)  = it2, ldots
  sched N (it1, it2, ldots)  = it2, ldots
  sched F (it1, it2, ldots)  = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  sched S (it1, it2, ldots)        = it1, it2, ldots
  sched N (it1, it2, ldots)        = it1, it2, ldots
  sched D (it1, it2, ldots)        = it2, ldots
  sched F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Scheduling policies}
\end{figure}

@@

\begin{theorem}[Termination Insensitive Non-Interference (TINI)]
  For any label |il| and configurations |ici = iconf iSi iti|, |ici' =
  iconf iSi' (fullconf idi ili tSi' ivi')|, where |i member {1,2}|, if
   $|ic1| \approx_{|il|} |ic2|$,
   $|ic1| |.->|^* |ic1'|$, and
   $|ic2| |.->|^* |ic2'|$, then
   $|ic1'| \approx_{|il|} |ic2'|$.
\end{theorem}
